The MacLeish Package: R Package for analyzing weather and spatial data

### 2022-06-07 joss_paper/paper.Rmd
added phenocamr

```{r phenocam, echo=FALSE, fig.cap="Image of the MacLeish Field Station taken above retrieved from the PhenoCam Network."}
knitr::include_graphics(here::here("joss_paper", "phenocam.jpeg"))
```

>>>>

```{r, eval=FALSE, include=FALSE}
download.file(phenocam(), here::here("joss_paper", "macleish_latest.jpg"))
```

```{r phenocam, echo=FALSE, fig.cap="Image of the MacLeish Field Station taken above retrieved from the PhenoCam Network."}
knitr::include_graphics(here::here("joss_paper", "macleish_latest.jpg"))
```
